\plaintitle

### 2025-05-21 docs/style/article-body.tex
small fix

\textbackslash begin\{table\}{[}ht{]}begin\{tabular\}\{\textbar c\textbar c\textbar c\textbar\} \hline \textbf{Bit size} \& \multicolumn{1}{c|}{\textbf{Teensy ($\mu s$)}} \& \multicolumn{1}{c|}{\textbf{Pico ($\mu s$)}} \textbackslash{} \hline 64 \& 13.1564 \& 106.3914 \textbackslash{} 512 \& 788.3139 \& 5302.4979 \textbackslash{} 1024 \& 3124.0580 \& 21111.2163 \textbackslash{} \hline

\caption{A brief overview of the testscript architecture.} \label{tab:iter1}

\textbackslash end\{tabular\} \label{tab:iter1}/end\{table\}

Table \ref{tab:iter1} presents the average execution time of iteration 1 on both Teensy 4.1 and Raspberry Pico Pi 2 across thre input sizes. The Teensy consistently outperforms the Pico, with the gap widening as the bit size increases.

@@

Additionally, the isolated effect of applying a single bitmask operation \texttt{\&\ 1} was evaluated. This resulted in a slight reduction in average execution time, from \texttt{13.1564\ µs} to \texttt{13.1000\ µs}, although this specific result is not included in the tables above.

@@

Table \ref{tab:iter3} presents the average execution time of iteration 3 on the Teensy 4.1 for varying batching and bit sizes. Additionally, when performing the same 1024/1024-bit operation, the Raspberry Pi Pico 2 showed average execution time of \texttt{80806.006\ µs} indicating a substantially lower throughput compared to the Teensy.

@@

In addition to the results presented in Table \ref{tab:iter4}, a further tests was conducted on the Teensy using a single-loop unrolled implementation for the 64-bit size, resulting in an average execution time of \texttt{6.6626\ µs}. An additional fully unrolled variant, where loops were entirely eliminated, produced a measured execution time of \texttt{0.0491\ µs}. However, this measurement was later determined to be invalid due to packaging error.

>>>>

\begin{table}[ht] \centering \caption{Execution times for different bit sizes on
Teensy and Pico} \label{tab:iter1} \begin{tabular}{|c|c|c|} \hline \textbf{Bit
size} & \textbf{Teensy ($\mu$s)} & \textbf{Pico ($\mu$s)} \\ \hline 64 & 13.1564
& 106.3914 \\ 512 & 788.3139 & 5302.4979 \\ 1024 & 3124.0580 & 21111.2163 \\
\hline \end{tabular} \end{table}

Table \ref{tab:iter1} presents the average execution time of iteration 1 on both Teensy 4.1 and Raspberry Pico Pi 2 across the input sizes. The Teensy consistently outperforms the Pico, with the gap widening as the bit size increases.

@@

Additionally, the isolated effect of applying a single bitmask operation \texttt{\&\ 1} was evaluated. This resulted in a slight reduction in average execution time, from \texttt{13.1564\ \$\textbackslash{}mu\ s\$} to \texttt{13.1000\ \$\textbackslash{}mu\ s\$}, although this specific result is not included in the tables above.

@@

Table \ref{tab:iter3} presents the average execution time of iteration 3 on the Teensy 4.1 for varying batching and bit sizes. Additionally, when performing the same 1024/1024-bit operation, the Raspberry Pi Pico 2 showed average execution time of \texttt{80806.006\ \$\textbackslash{}mu\ s\$} indicating a substantially lower throughput compared to the Teensy.

@@

In addition to the results presented in Table \ref{tab:iter4}, a further tests was conducted on the Teensy using a single-loop unrolled implementation for the 64-bit size, resulting in an average execution time of \texttt{6.6626\ \$\textbackslash{}mu\ s\$}. An additional fully unrolled variant, where loops were entirely eliminated, produced a measured execution time of \texttt{0.0491\ \$\textbackslash{}mu\ s\$}. However, this measurement was later determined to be invalid due to packaging error.
